Title

### 2013-01-09 inc/extension/initial_conditions/initial_conditions.tex
use Dowell calcuated initial transverse emission formulation

The single-photon photoemission analysis of Jensen \textit{et al.}\cite{jensen_theoretical_2006} indicates that for a metallic photocathode the transverse momentum variance at $ t = 0 $ is given by
\begin{equation} \label{eq:jensen_eta}
( \Delta p_{x} )^{2} = ( \Delta p_{y} )^{2} = \eta_{ \smallT } ( 0 ) \approx \frac{ m_{e} \epsilon_{\smallF} ( \hbar \omega - \Phi ) } { \hbar \omega + \epsilon_{\smallF} } \; \text{,}
\end{equation}
in the limit where the Fermi energy $ \epsilon_{\smallF} $ of the metal photocathode and excess photoemission energy, $ \Delta E = \hbar \omega - \Phi $ are significantly greater that the thermal energy $ k_{B} T $ of the electrons in the photocathode -- a condition that is generally met in laser-driven DC photoelectron guns.
From a simplistic viewpoint, only the electrons generated with positive longitudinal momentum will contribute to the pulse since those electrons generated with negative momentum do not leave the photocathode.
This implies that the uncertainty in the longitudinal direction is half that of the transverse directions; that is to say
\begin{equation}
( \Delta p_{ z } )^{2} = \left ( \frac{\Delta p_{ x , y }}{ 2 } \right )^{2} \text{,}
\end{equation}
so that
\begin{equation}
\eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 )}{ 4 } \; \text{.}
\end{equation}

These initial conditions at $t=0$ for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form}, will be used for the remainder of this paper.
\begin{subequations} \label{eq:summary}
\begin{gather}
\sigma_{ \smallT } ( 0 ) = \frac{ w^{ 2 } }{ 2 } \\
\sigma_{ z } ( 0 ) = \frac{ ( v_{{ \scriptscriptstyle 0}} \tau )^{ 2 } }{ 2 } \\
%alternative formulation + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
\gamma_{ \smallT } ( 0 ) = 0 \\
\gamma_{ z } ( 0 ) = 0 \\
\eta_{ \smallT } ( 0 ) = \frac{ m_{e} \epsilon_{ F } ( \hbar \omega - \Phi ) }{ 3 ( \hbar \omega + \epsilon_{ \smallF } ) } \\
\eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 ) }{ 4 }
\end{gather}
\end{subequations}

>>>>

The careful analysis of Dowell and Schmerge \cite{dowell_quantum_2009} indicates that for a metallic photocathode the transverse momentum variance at $ t = 0 $ is given by
\begin{equation} \label{eq:jensen_eta}
  \eta_{ \smallT } ( 0 ) \approx \frac{ m_{e} }{ 3 } ( \hbar \omega - \Phi ) \; \text{,}
\end{equation}
%in the limit where the Fermi energy $ \epsilon_{\smallF} $ of the metal photocathode and excess photoemission energy, $ \Delta E = \hbar \omega - \Phi $ are significantly greater that the thermal energy $ k_{B} T $ of the electrons in the photocathode -- a condition that is generally met in laser-driven DC photoelectron guns.
in the limit where the temperature is low enough to consider the system well described by Fermi-Dirac statistics where the chemical potential is nearly equal to the Fermi energy.
From a simplistic viewpoint, only the electrons generated with positive longitudinal momentum will contribute to the pulse since those electrons generated with negative momentum do not leave the photocathode.
This implies that the uncertainty in the longitudinal direction is half that of the transverse directions; that is to say
\begin{equation}
( \Delta p_{ z } )^{2} = \left ( \frac{\Delta p_{ x , y }}{ 2 } \right )^{2} \text{,}
\end{equation}
so that
\begin{equation}
\eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 )}{ 4 } \; \text{.}
\end{equation}

These initial conditions at $t=0$ for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form}, will be used for the remainder of this paper.
\begin{subequations} \label{eq:summary}
\begin{gather}
\sigma_{ \smallT } ( 0 ) = \frac{ w^{ 2 } }{ 2 } \\
\sigma_{ z } ( 0 ) = \frac{ ( v_{{ \scriptscriptstyle 0}} \tau )^{ 2 } }{ 2 } \\
%alternative formulation + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
\gamma_{ \smallT } ( 0 ) = 0 \\
\gamma_{ z } ( 0 ) = 0 \\
\eta_{ \smallT } ( 0 ) = \frac{ m_{e} } { 3 } ( \hbar \omega - \Phi ) \\
\eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 ) }{ 4 }
\end{gather}
\end{subequations}
